Papers

### 2025-02-19 papers.qmd
add publication details

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, accepted, 2024. [arxiv preprint](https://arxiv.org/abs/2305.08834)

>>>>

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, vol. 13, no. 1, 2025. [PDF](Papers/Francom-2025-Calibration-JUQ.pdf)
